---
title: "October 2020 CBASS qPCR Analysis"
author: "Rich"
date: "1/14/2021"
output: 
  html_document:
    code_folding: hide
  
---

```{r setup and load libraries, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message=FALSE, cache = TRUE, fig.width=6, fig.asp=.618, out.width='70%', fig.align='center')

#Tidy Data and Easy Wrangling
library(plyr)
library(dplyr)
library(tidyverse)
library(ggplot2)
library(stringr)
library(readxl)
library(lubridate)
library(devtools)
library(magrittr)
library(purrr)

library(kableExtra)
library(knitr)

#qPCR
library(steponeR)

#Basic Stats
library(broom)
library(rstatix)
library(emmeans)
library(multcomp)

```

## October 2020 qPCR CBASS Analysis

### Introduction: 

These samples were collected from the 32^o^C tanks (check) during the October 2020 Florida Keys CBASS cruise. Ross has already performed heat tolerance on the data.

All samples were run with A actin, Acer cam SYBR master mix and D GTMM

```{r load in data, include=FALSE}

plates <- list.files(path="qPCR/csv",pattern="csv$", full.names=TRUE)

data<-steponeR(files=plates, target.ratios=c('A.Acer', "D.Acer"),
               fluor.norm=list(A=0, D=0, Acer=0),
               copy.number=list(A=9, D=3, Acer=1),
               ploidy=list(A=1, D=1, Acer=2),
               extract=list(A=.813, D=0.813, Acer=.982))

data <- data$result

data %<>% separate(Sample.Name, into = c('Cruise', 'Nursery', 'SampleName'), sep = '_', remove = FALSE) %>%
  mutate('Species'=str_sub(SampleName, 1, 2), 'Genotype'=str_sub(SampleName, 3, length(SampleName)))

```

```{r QC, echo=TRUE}

# Show samples that didn't work
fails <- data %>%
  filter(Acer.reps!=2 | Acer.CT.sd>1.5 | A.CT.sd > 1.5)

rerun <- fails %>%
  filter(!is.na(Genotype)& Cruise!='NSF')

#Good data
data %<>% anti_join(., fails, by= 'Sample.Name')

#Check for D
dRerun <- data %>%
  filter(D.reps==2 & D.CT.sd>1.5 | D.reps==1)

#Change D
data %<>% mutate(D.Acer=ifelse(D.reps!=0 & D.CT.sd>1.5, NA, D.Acer))

# Set no detections to value below minimum detected value
data <- data %>%
  mutate(A.Acer = ifelse(is.na(A.Acer), min(A.Acer, na.rm = T) * 0.5, A.Acer),
         D.Acer = ifelse(is.na(D.Acer), min(D.Acer, na.rm = T) * 0.5, D.Acer))

data <- data %>%
  dplyr::select(Nursery, Species, Genotype, A.Acer, D.Acer, Acer.reps, A.reps, D.reps) %>%
  mutate(Species=ifelse(Species=='Ac', 'Acer', 'Apal'), 
         Dominant=ifelse(A.Acer>D.Acer & A.reps==2, 'A', 
                         ifelse(D.Acer>A.Acer & D.reps==2, 'D', 'A'))) 

```

```{r Basic Data plots, echo=TRUE}

p <- ggplot(data, aes(Nursery, log10(A.Acer))) +
  geom_violin(draw_quantiles = T)+
  geom_jitter(aes(color=Dominant)) +
  facet_wrap(~Species) +
  labs(x='Nursery', y='log10(SH)')

p

mod <- data %>%
  filter(Dominant=='A', Species=='Acer') %>%
  lm(log10(A.Acer) ~Nursery, data=.)

tidy(anova(mod)) 

pwpp(emmeans(mod, 'Nursery'))

```

### Basic Summary 

This is ~60% of the qPCR data that we have. The SH for the RRT Nursery is significantly higher than the rest. The was one sample from RRT that had detectable D and was dominant.

Follow up questions:

1. Was there a difference in thermal tolerance at RRT?