---
title: "October 2020 CBASS qPCR Analysis"
author: "Rich"
date: "1/14/2021"
output: 
  html_document:
    code_folding: hide
  
---

```{r setup and load libraries, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message=FALSE, cache = TRUE, fig.width=6, fig.asp=.618, out.width='70%', fig.align='center')

#Tidy Data and Easy Wrangling
library(plyr)
library(dplyr)
library(tidyverse)
library(ggplot2)
library(stringr)
library(readxl)
library(lubridate)
library(devtools)
library(magrittr)
library(purrr)

library(kableExtra)
library(knitr)

#qPCR
library(steponeR)

#Basic Stats
library(broom)
library(rstatix)
library(emmeans)
library(multcomp)

```

## October 2020 qPCR CBASS Analysis

### Introduction: 

These samples were collected from the 32^o^C tanks (check) during the October 2020 Florida Keys CBASS cruise. Ross has already performed heat tolerance on the data.

All samples were run with A actin, Acer cam SYBR master mix and D GTMM

```{r load in data, include=FALSE}

plates <- list.files(path="qPCR/csv",pattern="csv$", full.names=TRUE)

data<-steponeR(files=plates, target.ratios=c('A.Acer', "D.Acer"),
               fluor.norm=list(A=0, D=0, Acer=0),
               copy.number=list(A=9, D=3, Acer=1),
               ploidy=list(A=1, D=1, Acer=2),
               extract=list(A=.813, D=0.813, Acer=.982))

data <- data$result

data %<>% separate(Sample.Name, into = c('Cruise', 'Nursery', 'SampleName'), sep = '_', remove = FALSE) %>%
  mutate('Species'=str_sub(SampleName, 1, 2), 'Genotype'=str_sub(SampleName, 3, length(SampleName))) 

```

```{r QC, echo=TRUE}

# Show samples that didn't work
fails <- data %>%
  filter(Acer.reps!=2 | Acer.CT.sd>1.5 | A.CT.sd > 1.5)

# rerun <- fails %>%
#   filter(!is.na(Genotype)& Cruise!='NSF') %>%
#   mutate('Reason'='highSD')

#Good data
data %<>% anti_join(., fails, by= 'Sample.Name')

uniqueSamples <- data %>%
  filter(Sample.Name != c('+', 'NTC') & Cruise!='NSF' & !is.na(SampleName)) %>%
  dplyr::count(cc = interaction(Nursery, SampleName)) %>% filter(n >= 1)


# 
# #Check for D
# dRerun <- data %>%
#   filter(D.reps==2 | D.reps==1)%>%
#   mutate('Reason'='Dcheck')
# 
# reruns <- bind_rows(rerun, dRerun) %>%
#   dplyr::select(Nursery, SampleName, Reason, File.Name) 

#newReruns <- anti_join(reruns, originalReruns, by=c('Nursery', 'SampleName'))

#Change D
data %<>% mutate(D.Acer=ifelse(D.reps!=0 & D.CT.sd>1.5, NA, D.Acer))

#Duplicates ross way
dups <- data %>% dplyr::count(cc = interaction(Nursery, SampleName)) %>% filter(n >= 2)

# Choose run with lowest mean sd for C and D
selected <- data %>%
  filter(interaction(Nursery, SampleName) %in% dups$cc) %>%
  rowwise() %>%
  mutate(meanctsd = mean(c(A.CT.sd, Acer.CT.sd, D.CT.sd), na.rm = T)) %>%
  group_by(interaction(Nursery, SampleName)) %>%
  slice(which.min(meanctsd)) %>%
  mutate(FileNumber=str_sub(File.Name, str_length(File.Name)-5, str_length(File.Name)-4))
# Keep selected with other rows
df <- data %>%
  filter(!interaction(Nursery, SampleName) %in% dups$cc) %>%
  bind_rows(selected)

# Set no detections to value below minimum detected value
data <- df %>%
  mutate(A.Acer = ifelse(is.na(A.Acer), min(A.Acer, na.rm = T) * 0.5, A.Acer),
         D.Acer = ifelse(is.na(D.Acer), min(D.Acer, na.rm = T) * 0.5, D.Acer))

data <- data %>%
  filter(!is.na(SampleName)&Nursery!='7') %>%
  dplyr::select(Nursery, Species, Genotype, A.Acer, D.Acer, Acer.reps, A.reps, D.reps, File.Name) %>%
  mutate(Species=ifelse(Species=='Ac', 'Acer', 'Apal'), 
         Dominant=ifelse(A.Acer>D.Acer & A.reps==2, 'A', 
                         ifelse(D.Acer>A.Acer & D.reps==2, 'D', 'A')),
         SH=ifelse(Dominant=='A', log10(A.Acer), log10(D.Acer))) %>%
  convert_as_factor(., vars=c('Nursery', 'Species', 'Genotype', 'Dominant')) %>%
  droplevels(.)


```

```{r Basic Data plots, echo=TRUE}

p <- ggplot(data, aes(reorder(Nursery, -SH), SH)) +
  geom_violin(draw_quantiles = T)+
  geom_jitter(aes(color=Dominant)) +
  facet_wrap(~Species) +
  labs(x='Nursery', y='log10(SH)') +
  scale_color_brewer(palette = 'Dark2')

p

mod <- data %>%
  filter(Dominant=='A', Species=='Acer') %>%
  #split(.$Species) %>%
  lm(SH ~Nursery, data=.)

lsm <- emmeans(mod, 'Nursery')


anova(mod) %>% 
  kable() %>%
  kable_styling(bootstrap_options = c('striped', 'hover', 'condensed'), full_width = FALSE)

cld(lsm) %>%
  kable() %>%
  kable_styling(bootstrap_options = c('striped', 'hover', 'condensed'), full_width = FALSE)

pwpp(emmeans(mod, 'Nursery'))

```

```{r determine outliers, eval=FALSE}

outliers <- data %>%
  group_by(Species) %>%
  identify_outliers(SH)




newReruns <- outliers %>%
  mutate(Reason='Outlier') %>%
  dplyr::select(Nursery, Nursery, Genotype, Reason, File.Name) %>%
  bind_rows(., newReruns)

```


### Basic Summary 

All the samples have been through on qPCR and two nurseries have higher SH than the rest. Does this translate to differences in thermal tolerance. There is one outlier.

Follow up questions:

1. Was there a difference in thermal tolerance at RRT and UM?